### 2021-03-11 README.Rmd
Modified resdir to rundir and included option to vary final years of recruitment in the historicasl conditioning.

```{r example, echo=TRUE}
# a constant TAC example
starttime <- (Sys.time())
library(aMSE)
library(rutilsMH)
library(makehtml)
library(knitr)
# Obviously you should modify the resdir to suit your own computer
if (dir.exists("c:/Users/User/DropBox")) {
  ddir <- "c:/Users/User/DropBox/A_code/"
} else {
  ddir <- "c:/Users/Malcolm/DropBox/A_code/"
}
resdir <- paste0(ddir,"aMSEUse/conddata/generic")  # data and results directory
dirExists(resdir,make=TRUE,verbose=TRUE)
# equilibrium zone -------------------------------------------------------------
# You now need to ensure that there is, at least, a control.csv, and a 
# constantsdata.csv file in the data directory plus some other data .csv files
# depending on how conditioned you want the model to be. Templates for the
# correct format can be produced using ctrlfiletemplate(), datafiletemplate().
# In the meantime it is easier to use the included data file "zone".
data(zone)
# Of course, usually one would use data files, control.csv and a zone.csv, which is 
# listed as the datafile within the control.csv. 
# zone <- makeequilzone(resdir,"control2.csv") # normally would read in a file
    equiltime <- (Sys.time())   # let's change the initial depletion
    origdepl <-  c(0.30,0.31,0.29,0.32,0.30,0.31,0.29,0.32) 
zoneDD <- depleteSAU(zone$zoneC,zone$zoneD,zone$glb,origdepl,zone$product,len=12)
out <- prepareprojection(zone$zone1,zone$zoneC,zone$glb,zoneDD,zone$ctrl)
  zoneDR <- out$zoneDP
  projC <- out$projC
  zoneCP <- out$zoneC
  midtime <- (Sys.time())

  glb <- zone$glb
  ctrl <- zone$ctrl
  print(equiltime - starttime)
  print(midtime - equiltime)
  propD <- getzoneprops(zone$zoneC,zoneDD,glb,year=1)
  # round(propD,3)
# Do the replicates ------------------------------------------------------------
  inityr <- zone$zone1$projC$inityrs
  saunames <- zone$zone1$SAUnames
  sauindex <- zone$glb$sauindex
  pyrs <- projC$projyrs + projC$inityr
  B0 <- tapply(sapply(zone$zoneC,"[[","B0"),sauindex,sum)
  exB0 <- tapply(sapply(zone$zoneC,"[[","ExB0"),sauindex,sum)

  midtime <- (Sys.time())
mseproj <- applymcda(zoneCP,zoneDR,glb,ctrl,projC$projyrs,projC$inityrs)
sauzoneDP <- asSAU(mseproj,sauindex,saunames,B0,exB0)
  endtime <- (Sys.time())
  print(endtime - midtime)
# Now plot some results
  plotC <- function(nsau,saunames,reps,projyrs,plts=c(4,2)) {
    return(list(nsau=nsau,saunames=saunames,reps=reps,projyrs=projyrs,plts=plts))
  }

  saunames <- zone$zone1$SAUnames
  pyrs <- projC$projyrs + projC$inityr
  reps <- ctrl$reps
  label <- "Catches t"
  yrs <- 1:pyrs

plotconst <- plotC(nsau=length(saunames),saunames,reps,pyrs,plts=c(4,2))

plotprep(width=7,height=8,newdev=FALSE)
plotproj(sauzoneDP$cpue,"CPUE",plotconst,vline=projC$inityrs,addqnts=TRUE)

plotproj(sauzoneDP$saudeplsB,"Spawning Biomass Depletion",plotconst,vline=projC$inityrs,addqnts=TRUE)

plotproj(sauzoneDP$recS/1000,"Recruitment '000s",plotconst,vline=projC$inityrs,addqnts=TRUE)

plotproj(sauzoneDP$catS,"Catches t",plotconst,vline=projC$inityrs,addqnts=TRUE)

>>>>

```{r example, echo=TRUE}
# a constant TAC example
starttime <- (Sys.time())
library(aMSE)
library(rutilsMH)
library(makehtml)
library(knitr)
# Obviously you should modify the rundir to suit your own computer
if (dir.exists("c:/Users/User/DropBox")) {
  ddir <- "c:/Users/User/DropBox/A_code/"
} else {
  ddir <- "c:/Users/Malcolm/DropBox/A_code/"
}
rundir <- paste0(ddir,"aMSEUse/conddata/generic")  # data and results directory
dirExists(rundir,make=TRUE,verbose=TRUE)
# equilibrium zone -------------------------------------------------------------
# You now need to ensure that there is, at least, a control.csv, and a 
# constantsdata.csv file in the data directory plus some other data .csv files
# depending on how conditioned you want the model to be. Templates for the
# correct format can be produced using ctrlfiletemplate(), datafiletemplate().
# 
# Of course, usually one would use data files, control.csv and a zone.csv, which
# is listed as the datafile within the control.csv. These must be stored in 
# rundir. There are example control and data files in the DropBox folder:
# C:\Users\User\Dropbox\National abalone MSE\aMSE_files. Copy the control2.csv
# and zonewest.csv into you rundir. Then, assuming yo have the very latest
# version of aMSE = 5300, the following code should work. Recently both aMSE and
# makehtml have been altered so that all references to resdir have been changed
# to rundir, so both packages will need updating. See their respective GitHub
# readme pages for details.

# TasmanianHS.R should be in rundir, but during development is in data-raw
source(paste0(ddir,"aMSE/data-raw/","TasmanianHS.R"))
# generate equilibrium zone ----------------------------------------------------
starttime2 <- (Sys.time())
zone <- makeequilzone(rundir,"control2.csv",cleanslate = TRUE) # normally would read in a file
equiltime <- (Sys.time()); print(equiltime - starttime2)
# declare main objects ---------------------------------------------------------
glb <- zone$glb
ctrl <- zone$ctrl
zone1 <- zone$zone1
projC <- zone1$projC
condC <- zone1$condC
zoneC <- zone$zoneC
zoneD <- zone$zoneD
product <- zone$product
# add some tables and plots into rundir
biology_plots(rundir, glb, zoneC)
plotproductivity(rundir,product,glb)
numbersatsize(rundir, glb, zoneD)
# Condition on Fishery ---------------------------------------------------------
zoneDD <- dohistoricC(zoneD,zoneC,glob=glb,condC,sigR=1e-08,sigB=1e-08)
# save conditioned results -----------------------------------------------------
save(zoneDD,file=filenametopath(rundir,"zoneDD.RData"))
# Illustrate productivity
propD <- getzoneprops(zoneC,zoneDD,glb,year=47)
addtable(round(t(propD),4),"propertyDD.csv",rundir,category="zoneDD",caption=
           "Properties of zoneD after conditioning on historical catches.")
addtable(round(t(zoneDD$harvestR[45:47,]),4),"final_harvestR.csv",rundir,
         category="zoneDD",caption="Last three years of harvest rate.")
popdefs <- getlistvar(zone$zoneC,"popdef")
addtable(round(t(popdefs),3),"popdefs.csv",rundir,category="zoneDD",caption=
           "Population specific definitions")
# Prepare projections ----------------------------------------------------------
cmcda <- mcdahcr(arrce=condC$histCE,hsargs=hsargs,
                 yearnames=rownames(condC$histCE),saunames=glb$saunames)
pms <- cmcda$pms
multTAC <- cmcda$multTAC
#out <- prepareprojection(projC,zoneC,glb,zoneDD,ctrl,multTAC)
out <- prepareprojectionnew(projC=projC,condC=condC,zoneC=zoneC,glb=glb,
                            zoneDD=zoneDD,ctrl=ctrl,varyrs=6,
                            multTAC=multTAC,lastsigR = 0.25)

zoneDP <- out$zoneDP
projC <- out$projC
zoneCP <- out$zoneCP

zoneDP <- doTASprojections(ctrl,zoneDP,zoneCP,condC$histCE,glb,mcdahcr,hsargs)
# save more plots to rundir ----------------------------------------------------
out <- plotbysau(zoneDP,glb,rundir)

projtime <- Sys.time()
print(projtime - starttime)

# make results webpage ---------------------------------------------------------
replist <- list(starttime=as.character(starttime),endtime=as.character(projtime))

# Unhash the make_html command to generate the results webspage
# make_html(
#   replist = replist,
#   rundir = rundir,
#   width = 500,
#   openfile = TRUE,
#   runnotes = NULL,
#   verbose = FALSE,
#   packagename = "aMSE",
#   htmlname = "aMSE"
# )
